\documentclass[journal,twoside,web]{ieeecolor}
\usepackage{jsen}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{wrapfig}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\markboth{Spring 2020}
{Pathan Faisal Khan: Big Data Analytics}
\begin{document}
\title{Graphical Analysis for Big Data Analytics}
\author{Pathan Faisal Khan
\thanks{Under the supervision of Dr. Shagufta Henna, Letterkenny Institute of Technology, Letterkenny, CO. Donegal }
}

\IEEEtitleabstractindextext{
\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}

\end{IEEEkeywords}}

\maketitle

\section{Introduction}
\label{sec:introduction}
\IEEEPARstart{T}{his}


\begin{thebibliography}{9}
    \bibitem{1}“Resources - Whitepapers, Infographics \& Webinars | Domo.” [Online]. Available: https://www.domo.com/learn.
    
    \bibitem{2}C. Petrov, “Big Data Statistics 2019,” Tech Jury. [Online]. Available: https://techjury.net/stats-about/big-data-statistics
    
    \bibitem{3}“Domo Resource - Data Never Sleeps 7.0.” [Online]. Available: https://www.domo.com/learn/data-never-sleeps-7.
    
    \bibitem{4}“A Short History Of Big Data,” Datafloq. [Online]. Available: https://datafloq.com/read/big-data-history/239.
    
    \bibitem{5}E. Team, “How Netflix Uses Big Data to Drive Success,” inside BIGDATA, 20-Jan-2018.
    
    \bibitem{6}“Wikibon’s 2018 Big Data Analytics Trends and Forecast,” Wikibon Research, 28-Feb-2018. .
    
    \bibitem{7}“What is graph analytics?,” IBM Big Data \& Analytics Hub. [Online]. Available: https://www.ibmbigdatahub.com/blog/what-graph-analytics. [Accessed: 12-Dec-2019].
    
    \bibitem{8}A. Buluç and K. Madduri, “Parallel Breadth-First Search on Distributed Memory Systems,” p. 12.
    
    \bibitem{9}V. N. Rao and V. Kumar, “Parallel depth first search. Part I. Implementation,” Int J Parallel Prog, vol. 16, no. 6, pp. 479–499, Dec. 1987.
    
    \bibitem{10}M. Naumov, A. Vrielink, and M. Garland, “Parallel Depth-First Search for Directed Acyclic Graphs,” in Proceedings of the Seventh Workshop on Irregular Applications: Architectures and Algorithms - IA3’17, Denver, CO, USA, 2017, pp. 1–8.
    
    \bibitem{11}M. Kranjčević, D. Palossi, and S. Pintarelli, “Parallel Delta-Stepping Algorithm for Shared Memory Architectures,” arXiv:1604.02113 [cs], Apr. 2016.
    
    \bibitem{12}J. W. Kim, H. Choi, and S.-H. Bae, “Efficient Parallel All-Pairs Shortest Paths Algorithm for Complex Graph Analysis,” in Proceedings of the 47th International Conference on Parallel Processing Companion, New York, NY, USA, 2018, pp. 5:1–5:10.
    
    \bibitem{13}L. Fitina, J. Imbal, V. Uiari, N. Murki, and E. Goodyear, “An Application of Minimum Spanning Trees to Travel Planning,” vol. 12, p. 11, 2010.
    
    \bibitem{14}L. L. Sz, “Random Walks on Graphs: A Survey,” p. 46.
    
    \bibitem{15}M. Sharir, “A strong-connectivity algorithm and its applications in data flow analysis,” Computers \& Mathematics with Applications, vol. 7, no. 1, pp. 67–72, Jan. 1981.
    
    \bibitem{16}U. N. Raghavan, R. Albert, and S. Kumara, “Near linear time algorithm to detect community structures in large-scale networks,” Phys. Rev. E, vol. 76, no. 3, p. 036106, Sep. 2007.
    
    \bibitem{17}R. Tarjan, “Depth-First Search and Linear Graph Algorithms,” SIAM J. Comput., vol. 1, no. 2, pp. 146–160, Jun. 1972.
    
    \bibitem{18}A. Monge and C. Elkan, An Efficient Domain-Independent Algorithm for Detecting Approximately Duplicate Database Records. 1997.
    
    \bibitem{19}Y. An, J. Janssen, and E. E. Milios, “Characterizing and Mining the Citation Graph of the Computer Science Literature,” Know. Inf. Sys., vol. 6, no. 6, pp. 664–678, Nov. 2004.
    
    \bibitem{20}V. D. Blondel, J.-L. Guillaume, R. Lambiotte, and E. Lefebvre, “Fast unfolding of communities in large networks,” J. Stat. Mech., vol. 2008, no. 10, p. P10008, Oct. 2008.
    
    \bibitem{21}H. Lu, M. Halappanavar, and A. Kalyanaraman, “Parallel Heuristics for Scalable Community Detection,” arXiv:1410.1237 [physics], Oct. 2014.
    
    \bibitem{22}T. Schank and D. Wagner, “Finding, Counting and Listing All Triangles in Large Graphs, an Experimental Study,” in Experimental and Efficient Algorithms, vol. 3503, S. E. Nikoletseas, Ed. Berlin, Heidelberg: Springer Berlin Heidelberg, 2005, pp. 606–609.
    
    \bibitem{23}H. C. Johnston, “Cliques of a graph-variations on the Bron-Kerbosch algorithm,” International Journal of Computer and Information Sciences, vol. 5, no. 3, pp. 209–238, Sep. 1976.
    
    \bibitem{24}S. C. Antoro, K. A. Sugeng, and B. D. Handari, “Application of Bron-Kerbosch algorithm in graph clustering using complement matrix,” presented at the International Symposium On Current Progress In Mathematics And Sciences 2016 (ISCPMS 2016): Proceedings of the 2nd International Symposium on Current Progress in Mathematics and Sciences 2016, Depok, Jawa Barat, Indonesia, 2017, p. 030141.
    
    \bibitem{25}L. C. Freeman, “Centrality in social networks conceptual clarification,” Social Networks, vol. 1, no. 3, pp. 215–239, Jan. 1978.
    
    \bibitem{26}Phillip Bonacich Reviewed, “Power and Centrality: A Family of Measures,” American Journal of Sociology, vol. 92, no. 5, pp. 1170–1182, 1987.
    
    \bibitem{27}C. F. A. Negre et al., “Eigenvector centrality for characterization of protein allosteric pathways,” Proc Natl Acad Sci U S A, vol. 115, no. 52, pp. E12201–E12208, Dec. 2018.
    
    \bibitem{28}L. Katz, “A new status index derived from sociometric analysis,” Psychometrika, vol. 18, no. 1, pp. 39–43, Mar. 1953.
    
    \bibitem{29}L. Page, S. Brin, R. Motwani, and T. Winograd, “The PageRank Citation Ranking: Bringing Order to the Web.,” 11-Nov-1999. [Online]. Available: http://ilpubs.stanford.edu:8090/422/. [Accessed: 12-Dec-2019].
    
    \bibitem{30}G. Sabidussi, “The centrality index of a graph,” Psychometrika, vol. 31, no. 4, pp. 581–603, Dec. 1966.
    
    \bibitem{31}S. P. Borgatti, “Centrality and network flow,” Social Networks, vol. 27, no. 1, pp. 55–71, Jan. 2005.
    
    \bibitem{32}L. C. Freeman, “A Set of Measures of Centrality Based on Betweenness,” Sociometry, vol. 40, no. 1, pp. 35–41, 1977.
    
    \bibitem{33}Z. Wu, S. Pan, F. Chen, G. Long, C. Zhang, and P. S. Yu, “A Comprehensive Survey on Graph Neural Networks,” arXiv:1901.00596 [cs, stat], Dec. 2019.
    
    \bibitem{34}F. Scarselli, M. Gori, Ah Chung Tsoi, M. Hagenbuchner, and G. Monfardini, “The Graph Neural Network Model,” IEEE Trans. Neural Netw., vol. 20, no. 1, pp. 61–80, Jan. 2009.
    
    \bibitem{35}“Special Issue on Graph-based Methods for Large Scale Financial and Business Data Analysis - Call for Papers - Elsevier.” [Online]. Available: https://www.journals.elsevier.com/pattern-recognition/call-for-papers/graph-based-methods. [Accessed: 09-Dec-2019].    
\end{thebibliography}

\end{document}
